final_project_draft

### 2022-03-28 draft.Rmd
March 28 graded after class commit. Fixed lollipop graph and made table.

## Political Donations of Professional Sports Team Owners 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
library(ggthemes)
pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")
pol_donations <- pol_donations %>% rename(year = 'Election Year') %>% mutate(amount = parse_number(Amount)) 
library(plotly)
```

@@

frequent <- pol_donations %>% group_by(Owner) %>%
    mutate(n = n()) %>%
    filter(n >= 65) %>%
  arrange(n) %>%
  mutate(donations = as.numeric(n)) %>%
  mutate(order = fct_reorder(.f = Owner, .x = donations))

plot1 <- ggplot(data = frequent, aes(x = amount, y = order, label = Amount, colour = League)) +
  geom_point() +
  labs(title = "Owners Who Have Made the Most Donations",
       y = "Owners",
       x = "Amount Donated",
       colour = "League") +
  theme_fivethirtyeight() +
  scale_colour_brewer(palette = "Dark2")

plot2 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = "Amount Donated",
       y = "Owner",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
  theme_fivethirtyeight()  +
  scale_colour_manual(values = c("red", "blue", "yellow"))

@@

@@

plot3 <- ggplot(data = nirvana, aes(x = popularity, y = order, label = Release_Date)) +
  geom_point() +
  geom_segment(aes(x = popularity, xend = popularity, y = 0, yend = order)) +
  coord_flip() +
  labs(x = "Popularity",
       y = "Song Title",
       title = "Most Popular Nirvana Songs")

>>>>

## Political Donations of Professional Sports Team Owners 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
library(ggthemes)
pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")
pol_donations <- pol_donations %>% rename(year = 'Election Year') %>% mutate(amount = parse_number(Amount)) 
pol_donations
library(plotly)
```

plot1 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = "Amount Donated",
       y = "Owner",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
  theme_fivethirtyeight()  +
  scale_colour_manual(values = c("red", "blue", "yellow"))

@@

frequent <- pol_donations %>% group_by(Owner) %>%
    mutate(n = n()) %>%
    filter(n >= 65) %>%
  arrange(desc(n)) %>%
  mutate(donations = as.numeric(n))

test <- frequent %>% mutate(owner = fct_reorder(.f = Owner, .x = n))
test2 <- frequent %>% mutate(owner = fct_inorder(Owner))

plot2 <- ggplot(data = test2, aes(x = amount, y = owner, label = Amount, colour = League)) +
  geom_point() +
  labs(title = "Owners Who Have Made the Most Donations",
       y = "Owners",
       x = "Amount Donated",
       colour = "League") +
  theme_fivethirtyeight() +
  scale_colour_brewer(palette = "Dark2")

@@

## Going off Second Political Donations Visualization
```{r}
library(knitr)
library(pander)
library(tidyverse)

owner_rank2 <- pol_donations %>% group_by(Owner, Team) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 65)

kable(owner_rank2, caption = "Frequency of Donations",
      col.names = c("Owner", "Team", "Amount of Donations Made"))
```

## Examining Top Donator 
```{r}
charles_johnson <- pol_donations %>% filter(Owner == "Charles Johnson") %>%
  filter(year == 2016 | year == 2018 | year == 2020)

ggplot(data = charles_johnson, aes(x = amount)) +
  geom_freqpoly()

charles_johnson %>% group_by(Recipient, amount) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

ggplot(data = charles_johnson, aes(x = amount, y = ))
```

@@

plot3 <- ggplot(data = nirvana, aes(x = order, y = popularity, label = popularity, colour = popularity)) +
  geom_point() +
  geom_segment(aes(x = order, xend = order, y = 0, yend = popularity)) +
  coord_flip() +
  labs(title = "Most Popular Nirvana Songs",
       colour = "Popularity") +
  theme_fivethirtyeight() +
  scale_colour_viridis_b()
